---
title: "P1805_hw5_jn2761"
author: "jiaying Ning"
date: "11/14/2020"
output: html_document
---


```{r setup, include=FALSE}
#loading package
library(tidyverse)
library(readxl)
library(janitor)
library(dplyr)
library(ggridges)
library(purrr)
library(broom)
library(patchwork)



knitr::opts_chunk$set(
  fig.width = 6,
    fig.asp = .6,
  out.width = "90%"

)

theme_set(theme_minimal()+theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_color_discrete = scale_color_viridis_d
scale_fill_discrete =scale_fill_viridis_d
```



## problem 2

##### Import data
```{r, error = TRUE}
#Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time
df = 
  tibble(
    path = list.files("data"), #created a dataframe containing all file names
  ) %>% 
  mutate(
    path = str_c("data/", path),
    data = map(path,read.csv)) %>% #Iterate over file names and read in data for each subject using purrr::map and saving the result as a new variable in the dataframe
  unnest() %>% 
   mutate(path=gsub("data/","",path), #reformat data
          path=gsub(".csv","",path)) %>%
   separate(path, c("control_arm","subject_id"), sep = "([_])") %>%
  relocate(subject_id,control_arm) %>%
   pivot_longer( #Tidy the result; manipulate file names to include control arm and subject ID
    week_1:week_8,
    names_to = "week", 
    names_prefix = "week_",
    values_to = "observation")


```

##### plot 1:spaghetti plot showing observations on each subject over time, and comment on differences between groups.

```{r}
df %>%
  group_by(subject_id)%>%
  ggplot(aes(x=week,y=observation,group=subject_id,color=subject_id))+
  geom_line() +
  stat_smooth(aes(group = 1),method = "lm", se = FALSE)+
  facet_grid(. ~ control_arm)
```

```{r}
exp = df %>%
  group_by(control_arm,subject_id)%>%
  filter(control_arm=="exp")
```


##### plot 2:spaghetti plot showing observations on each subject over time, and comment on differences between groups.

```{r}
df %>%
  group_by(control_arm,subject_id)%>%
  filter(control_arm=="con")%>%
  ggplot(aes(x=week,y=observation,group=subject_id,color=control_arm))+
  geom_line() +
  geom_line(aes(x=exp$week,y=exp$observation,group=exp$subject_id,color=exp$control_arm))
```


**Overall, observation value seems to be higher as time pass by for the experimental group, and there seems to no correlation between time and observations for the control group.**


## problem3




making sure the table I am trying to create work before putting into function
```{r}
tidy(t.test(rnorm(n=30,mean=0,sd=5))) %>%
  select(p.value) %>%
  mutate(x=list(rnorm(n=30,mean=0,sd=5)),
         mu=0,
         mean = mean(x[[1]]))%>%
 select(-x)
```

creating function that produce table that shows p.value, true mu, and sample mean for different true mu.
```{r}


sim_norm = function(size=30, mu, sigma = 5) {
  
  
tidy(t.test(rnorm(n=size, mean = mu, sd = sigma)),mu = 0,conf,leve=0.95,alternative="two.sided") %>%
  select(p.value) %>%
  mutate(x=list(rnorm(n=size, mean = mu, sd = sigma)),
         mean = mean(x[[1]]))%>%
 select(-x)
  
  
}


```





try to simulate data, sumulate data with mu=0 first, created 5000 dataset with true mean=0
```{r}

mu_c =c(1:7)
output = vector("list", length = 6)


  output[[1]] =  rerun(5000, sim_norm(mu = mu_c[1]-1)) %>%
  bind_rows()
  
  output[[1]] 

```


testing for loop for simulating  10 dataset for mu from 0~6

```{r}


for (i in 1:7) {
  output[[i]] =  rerun(10, sim_norm(mu = mu_c[i]-1)) %>%
  bind_rows()}

```


creating datframe containing true mean(0-6), p-value for each simulated dataset,and sample mean

```{r}


sample_results = 
tibble(
  mu_c =c(1:7)
) %>%
  mutate(
    output_list = map(.x = mu_c-1,~rerun(5000,sim_norm(mu=.x))), #function inside of a function #rerun a 100 times
    estmate_df = map(output_list, bind_rows)
  )  %>%
  select(-output_list) %>% #i dont want this anymore 
  unnest(estmate_df) %>%
  mutate(decision = ifelse(p.value<0.05,"reject","accept"), #adding categorical variable decision to mark whether each sample is rejected or accepted from null
         mu_c=mu_c-1)

```



##### plot showing the proportion of times the null was rejected (the power of the test) on the y axis and the true value of μ on the x axis

```{r}
sample_results%>%
  group_by(decision,mu_c) %>%
  filter(decision=="reject") %>%
  summarise(n_reject=n()) %>%
   mutate(freq_reject= n_reject/5000)%>%
  ggplot(aes(x=mu_c, y=freq_reject,fill=mu_c)) + 
  geom_bar(stat = "identity") +
  scale_x_continuous(
    breaks = c(0:6)) +
  scale_y_continuous(
   n.breaks = 20) +
  labs(titles = "the proportion of time null-hypothesis is rejected",
        x = "true value of μ",
       y= " rejection with null mean=0") +
  theme(legend.position = "right")



  
```

 **As the true mean increase, we can see that the proportion of time we reject the test with null (mu=0) also increase. which means that the power of the test increase as the true mean deviate away from the hypothesis mean. **


##### plot showing the average estimate of μ̂  on the y axis and the true value of μ on the x axis
```{r}
dist_mean_all=
sample_results%>%
  ggplot(aes(x=as.factor(mu_c), y=mean,fill=mu_c)) + 
  geom_violin()+
  labs(titles = "true μ versus average estimate of μ for all",
        x = " the true value of μ",
       y= " average estimate of μ") +
  theme(legend.position = "right")
  
```

##### plot showing the average estimate of μ̂  only in samples for which the null was rejected on the y axis and the true value of μ on the x axis

```{r}

dist_mean_reject=
sample_results%>%
   filter(decision=="reject") %>%
  ggplot(aes(x=as.factor(mu_c), y=mean,fill=mu_c)) + 
  geom_violin() +
  labs(titles = "true μ versus average estimate of μ for rejected",
        x = " the true value of μ",
       y= " average estimate of μ") +
  theme(legend.position = "right")
  
```


```{r}
dist_mean_all+dist_mean_reject
```



```{r}
all=
sample_results%>%
  group_by(mu_c)%>%
  summarise(mean_mu = mean(mean),n=n()) 


reject=
sample_results%>%
    filter(decision =="reject") %>%
  group_by(mu_c)%>%
  summarise(mean_mu = mean(mean),n=n())  

```

```{r}

accept_reject=
sample_results%>%
  group_by(mu_c,decision)%>%
  summarise(mean_mu = mean(mean),n=n())  %>%
 ggplot(aes(x=mu_c, y=mean_mu,color=decision)) + 
  geom_point(aes(size=n,alpha=0.2,shape=decision)) +
  theme(legend.position = "right")+
labs(titles = " average estimate of μ̂ versus true value of μ between accepted and rejected ",
        x = "true value of μ",
       y= " average estimate of μ") +
  theme(legend.position = "right")



```


```{r}

all_reject=
ggplot() + 
  geom_point(data = all, aes(x = mu_c,y=mean_mu,size=n), 
                color = "blue", alpha = 0.3) + 
    geom_point(data = reject, aes(x = mu_c,y=mean_mu,size=n), 
                color = "red", alpha = 0.3) +
  labs(titles = " average estimate of μ̂ versus true value of μ between all and those that are rejected ",
        x = "true value of μ",
       y= " average estimate of μ") +
  theme(legend.position = "right")
  
```


```{r}
accept_reject+all_reject
```



